---
title: "Data Story Example Slides"
format: revealjs
---

## Slide-deck for your presentation

::: {.incremental}
- This is an exmple file for a slide-deck of a data story in a *narrative structure*. 
    - See *Effective Data Storytelling*, Brent Dykes (2020), Figure 4.3.
- **Narrative structure** means, that the slide-deck can be used to tell a story in a **linear way** in front of an audience while going through the slides.  
- This slidedeck is made with quarto revealjs. Documentation: [Quarto > Presentations > Revealjs](https://quarto.org/docs/presentations/revealjs/)
- It is written a bit similar to a report. Each `## Headline` becomes a slide title and defines a slide. You just use less text, more often in lists, and more visuals. 
- You can go interactive easily because it is HTML. 
:::


## Visuals

```{r}
#| echo: false # This shows no code

library(tidyverse)
df <- read_csv("data/country_panel_wdi_who.csv", show_col_types = FALSE)
df |>
  filter(year %in% c(1978, 1998, 2018)) |>
  ggplot(aes(
    x = gdp_per_capita_usd,
    y = life_expectancy_years,
    size = total_population,
    color = region
  )) +
  geom_point(alpha = 0.8) +
  scale_x_log10(breaks = c(300, 3000, 30000)) +
  scale_y_continuous(limits = c(40, 87)) +
  scale_size_area(max_size = 15) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~year) +
  labs(x = "GDP per capita (USD)", y = "Life expectancy (years)") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.border = element_rect(),
    aspect.ratio = 1
  ) +
  guides(
    size = "none",
    color = guide_legend(ncol = 4, override.aes = list(size = 4), title = NULL)
  )
``` 



## More visuals

```{r}
df |>
  filter(year == 2016, total_population > 20000000) |>
  summarize(
    mean_var = mean(life_expectancy_years),
    .by = c(country_name, region)
  ) |>
  arrange(mean_var) |>
  ggplot(aes(
    x = mean_var,
    y = country_name |> fct_inorder(),
    fill = region
  )) +
  geom_col() +
  labs(
    title = "Life Expectancy, Countries with more than 20 Mio.",
    x = "",
    y = "",
    fill = ""
  ) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal(base_size = 8.5)
```