---
title: "Scrollytelling"
author: "Names"
format: closeread-html
---

This is an example of Data Scrollytelling using the quarto extension [`closeread`](https://closeread.dev).

::: {.callout-note}
There is a Student Scrolly-Telling Competition with a deadline fitting for your project!
:::

```{r}
#| label: packages
#| message: false

# These are the packages used in the report
library(tidyverse)
```

:::{.cr-section}

Let us look at a bubble plot in the style of Hans Rosling. @cr-bubble1

Each bubble represents a country. The bubble size represents the population. 

:::{#cr-bubble1}
```{r}
#| warning: false 

df <- read_csv("data/country_panel_wdi_who.csv", show_col_types = FALSE)

df |>
  filter(year %in% c(2018)) |>
  ggplot(aes(
    x = gdp_per_capita_usd,
    y = life_expectancy_years,
    size = total_population,
    color = region
  )) +
  geom_point(alpha = 0.8) +
  scale_x_log10(breaks = c(300, 3000, 30000), limits = c(200, 60000)) +
  scale_y_continuous(limits = c(40, 87)) +
  scale_size_area(max_size = 15) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "In the year 2018",
    x = "GDP per capita (USD)",
    y = "Life expectancy (years)"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", panel.border = element_rect()) +
  guides(
    size = "none",
    color = guide_legend(ncol = 4, override.aes = list(size = 4), title = NULL)
  )
```
:::

40 years before the cloud looked differently. @cr-bubble2 

:::{#cr-bubble2}
```{r}
#| warning: false 

df <- read_csv("data/country_panel_wdi_who.csv", show_col_types = FALSE)

df |>
  filter(year %in% c(1978)) |>
  ggplot(aes(
    x = gdp_per_capita_usd,
    y = life_expectancy_years,
    size = total_population,
    color = region
  )) +
  geom_point(alpha = 0.8) +
  scale_x_log10(breaks = c(300, 3000, 30000), limits = c(200, 60000)) +
  scale_y_continuous(limits = c(40, 87)) +
  scale_size_area(max_size = 15) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "In the year 1978",
    x = "GDP per capita (USD)",
    y = "Life expectancy (years)"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom", panel.border = element_rect()) +
  guides(
    size = "none",
    color = guide_legend(ncol = 4, override.aes = list(size = 4), title = NULL)
  )
```
:::



Over the years the cloud of bubbles moved upward and rightward into the healthier and wealthier corner. @cr-bubbles 

[@cr-bubbles]{scale-by="1.5"} 


:::{#cr-bubbles}
```{r}
#| warning: false 

df <- read_csv("data/country_panel_wdi_who.csv", show_col_types = FALSE)

df |>
  filter(year %in% c(1978, 1998, 2018)) |>
  ggplot(aes(
    x = gdp_per_capita_usd,
    y = life_expectancy_years,
    size = total_population,
    color = region
  )) +
  geom_point(alpha = 0.8) +
  scale_x_log10(breaks = c(300, 3000, 30000)) +
  scale_y_continuous(limits = c(40, 87)) +
  scale_size_area(max_size = 15) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~year) +
  labs(x = "GDP per capita (USD)", y = "Life expectancy (years)") +
  theme_minimal() +
  theme(legend.position = "bottom", panel.border = element_rect()) +
  guides(
    size = "none",
    color = guide_legend(ncol = 4, override.aes = list(size = 4), title = NULL)
  )
```
:::


:::

## Now a regular HTML continues

```{r}
#| label: fig-lifeexpectancy
#| fig-height: 7
#| fig-cap: "*This is just a placeholder.*"

df |>
  filter(year == 2016, total_population > 20000000) |>
  summarize(
    mean_var = mean(life_expectancy_years),
    .by = c(country_name, region)
  ) |>
  arrange(mean_var) |>
  ggplot(aes(
    x = mean_var,
    y = country_name |> fct_inorder(),
    fill = region
  )) +
  geom_col() +
  labs(
    title = "Life Expectancy, Countries with more than 20 Mio.",
    x = "",
    y = "",
    fill = ""
  ) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal()
```
